---
title: "Project2 Drug Abuse CT"
author: "JM"
date: "March 12, 2017"
output: html_document
---

### Basic Setup
```{r setup, include=FALSE, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
install.packages("knitr")
```

### Set up libraries
```{r}
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
#library(ggmap)
```

### Read Data and Select Relevant Columns
```{r}
AllAbuseData <- read.csv(file="C:/MSDA/D607/Project2/DrugFatalitiesCT/Accidental_Drug_Related_Deaths__2012-2016.csv")
head(AllAbuseData)
names(AllAbuseData)
```

## Tidy And Analyse the data for Drug cause
```{r}
DeathCauseTidy <- select(AllAbuseData, CaseNumber, Heroin:Other)
DeathCauseTidy <- DeathCauseTidy %>% gather(DrugName, Present, Heroin:Other)
DeathCauseTidy <- DeathCauseTidy %>% filter(Present!="") %>% select(CaseNumber, DrugName)
DeathCauseTidy <- DeathCauseTidy %>% group_by(DrugName) 
DeathCauseDrugCount <- DeathCauseTidy %>% summarise(count=n())
head(DeathCauseDrugCount)
```

## Tidy And Analyse the data for Race Background
```{r}
BackgroundTidy <- select(AllAbuseData, CaseNumber, Sex, Race, Age)
BackgroundTidy
RaceTidy <- BackgroundTidy %>% separate(Race, sep=",", into = c("PrimaryRace","SecondaryRace"))
RaceTidy
PrimaryRaceCount<-RaceTidy %>% group_by(PrimaryRace) %>% summarise(count=n())
colnames(PrimaryRaceCount)[1]<-"Race"
PrimaryRaceCount$Race<-trimws(PrimaryRaceCount$Race)
PrimaryRaceCount
SecRaceCount<-RaceTidy %>% group_by(SecondaryRace) %>% summarise(count=n())
colnames(SecRaceCount)[1]<-"Race"
SecRaceCount$Race<-trimws(SecRaceCount$Race)
AllRaceCount <- left_join(x=PrimaryRaceCount, y=SecRaceCount, "Race")
AllRaceCount$count.y[is.na(AllRaceCount$count.y)] <- 0
AllRaceCount
AllRaceCount <- AllRaceCount %>% mutate(total=count.x+count.y)
AllRaceCount %>% arrange(total)
```
### The biggest abuse is seen in WHITE population. But this needs to be further analysed in terms of state population to ascertain what percentage of population of a specific Race is more affected.

## Tidy And Analyse the data for Age Background
```{r}
BackgroundTidy <- select(AllAbuseData, CaseNumber, Age)
BackgroundTidy<-BackgroundTidy %>% mutate(Age=as.integer(Age))
BackgroundTidy
BackgroundTidyBelow20 <- BackgroundTidy %>%  filter(Age<=20) %>% summarise(count=n())
BackgroundTidyBelow20$AgeGroup <- "Below20"
BackgroundTidy2140 <- BackgroundTidy %>%  filter(Age>20 & Age<=40) %>% summarise(count=n())
BackgroundTidy2140$AgeGroup <- "21-40"
BackgroundTidy4160 <- BackgroundTidy %>%  filter(Age>40 & Age<=60) %>% summarise(count=n())
BackgroundTidy4160$AgeGroup <- "41-60"
BackgroundTidyAbove60 <- BackgroundTidy %>%  filter(Age>60) %>% summarise(count=n())
BackgroundTidyAbove60$AgeGroup <- "Above60"
AllAgeGroups <- bind_rows(BackgroundTidyBelow20, BackgroundTidy2140, BackgroundTidy4160, BackgroundTidyAbove60)
AllAgeGroups <- AllAgeGroups[c("AgeGroup", "count")]
AllAgeGroups

```
### As noted above no major difference seen in drug abuse between Ages above and below 40. 