---
title: "Project2 VotingRecords"
author: "JM"
date: "March 12, 2017"
output: html_document
---


### Basic Setup
```{r setup, include=FALSE, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
install.packages("knitr")
```

### Set up libraries
```{r}
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
#library(ggmap)
```

### Read Data and Select Relevant Columns
```{r}
AllVotingRecords <- read.csv(file="C:/MSDA/D607/Project2/house-votes-84.data.txt", header=FALSE)
Headers <- read.csv(file="C:/MSDA/D607/Project2/house-headers.txt", header=FALSE)
head(AllVotingRecords)
Headers<-unlist(Headers)
Headers<-trimws(Headers)
Headers<- gsub("-", "_", Headers)
Headers<- gsub(" ", "_", Headers)
colnames(AllVotingRecords) <- Headers
names(AllVotingRecords)
head(AllVotingRecords)
```

### Tidy The data 
```{r}
head(AllVotingRecords)
AllVotingRecordsTidy <- AllVotingRecords %>% gather(Issue, VoteType, handicapped_infants:export_administration_act_south_africa)
AllVotingRecordsTidy <- AllVotingRecordsTidy %>% filter(VoteType!="?")
AllVotingRecordsTidy1 <- AllVotingRecordsTidy %>% unite(NewClass,sep="_", Class_Name, VoteType)
head(AllVotingRecordsTidy1)
AllVotingRecordsTidy2<- AllVotingRecordsTidy1 %>% group_by(Issue,NewClass) %>% summarise(count=n())
AllVotingRecordsTidy2 <- AllVotingRecordsTidy2 %>% spread(NewClass, count)
head(AllVotingRecordsTidy2)
```
### Analyse the data to find issues of difference and common ground
```{r}
AllVotingRecordsTidy3 <- AllVotingRecordsTidy2 %>% mutate(DemocratAyes=democrat_y/(democrat_n+democrat_y) * 100) %>% mutate(RepublicanAyes=republican_y/(republican_y+republican_n) * 100) %>% select(Issue, DemocratAyes, RepublicanAyes)
head(AllVotingRecordsTidy3)
AllVotingRecordsTidy4<-AllVotingRecordsTidy3 %>% mutate(Differential=DemocratAyes-RepublicanAyes)
head(AllVotingRecordsTidy4)
summary(AllVotingRecordsTidy4$Differential)
```
## Issues of Most Difference
```{r}
VotingRepubFavorite<-AllVotingRecordsTidy4 %>% arrange(Differential)
VotingDemoFavorite<-AllVotingRecordsTidy4 %>% arrange(desc(Differential))
head(VotingRepubFavorite)
head(VotingDemoFavorite)
```
### As noted issues of most difference are Physician_free_freeze and el_savlador_aid where Republicans favor and AdoptionOfBudget and Aid to Nicaragua where Republicans favor
## Issues of Common ground
```{r}
VotingBothFavorite<-AllVotingRecordsTidy4 %>% filter(Differential<10 & Differential>-10)
head(VotingBothFavorite)
```
### As noted the issue of consenus are Immigration (this was 1980s !!!!) and Water project sharing
