---
title: "DATA 607 HW3"
author: "JM"
date: "February 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CHAPTER 8 QS 3
### Extract the names
```{r}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```
### Reorder the first and second names 
```{r}
first_second <- str_split(name, ", ")
first_second <- sapply(first_second, function(x) str_replace(paste(x[2], x[1]),"^NA ",""))
title_regex <- "^(Mr|Mrs|Dr|Rev)\\."
name_wo_title<-str_replace(first_second, title_regex, "")
name_wo_title
```
### Detect which have the titles - the vector
```{r}
str_detect(first_second, title_regex)
```
### Detect which have the second names
```{r}
name_wo_title[str_detect(name_wo_title, "\\b[a-zA-Z]\\b")]
```


## CHAPTER 8 QS 4
Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.

### (a) [0-9]+\\$ is for Money (digits followed by $)
```{r}
samples <- c('123$', '456$', 8900)
str_match(samples, "[0-9]+\\$")
```
### (b) \\b[a-z]{1,4}\\b is first instance of a word of size 1 to 4 that sit inside a sentence.
```{r}
samples <- c('Here we go', 'Oye', 8900, 'I will not forgive you Mr. 500.')
str_match(samples, "\\b[a-z]{1,4}\\b")
```
### (c) .*?\\.txt$ is for filenames with extension txt
```{r}
samples <- c('abc.csv', 'Tex.txt', '8900.txt', 7200, 'Wer$234.txt')
str_match(samples, ".*?\\.txt$")
```

### (d) \\d{2}/\\d{2}/\\d{4} is for dd/dd/dddd - a rather non-strict representation of date
```{r}
samples <- c('22/12/2008', 'Tex.txt', '8900/12/12', '12/1/7200', '90/90/9000')
str_match(samples, "\\d{2}/\\d{2}/\\d{4}")
```
### (e) <(.+?)>.+?</\\1> is for xml opening and closing tags, though strictly speaking xml tags do not allow many special characters as shown below.
```{r}
samples <- c('<abcd>.xx</abcd>.', '<xxx>Tex.txt</xxx>', '<root>8900.txt', 7200, '<456->Wer$234.txt</456->')
str_match(samples, "<(.+?)>.+?</\\1>")
```

## CHAPTER 8 QS 9
The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.
clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}
raw.data1 <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

```
### Lets assume this is a message in english and is a transformation which is done by mapping the alphabets to an another set

### SEARCH FOR SPACE - would be one of most commonly occuring character
```{r}
sort(table(str_extract_all(raw.data1, ".")), decreasing=TRUE)[1:10]
```

### So let's search for most commonly used three letter words - 'and' and 'the'. For this let's what three letter groups are most repeating in the given messae.
```{r}
str_extract_all(raw.data1, "c...c")
str_extract_all(raw.data1, "5...5")
str_extract_all(raw.data1, "o...o")
str_extract_all(raw.data1, "w...w")
str_extract_all(raw.data1, "g...g")
str_extract_all(raw.data1, "n...n")
str_extract_all(raw.data1, "f...f")
str_extract_all(raw.data1, "j...j")
str_extract_all(raw.data1, "r...r")
str_extract_all(raw.data1, "t...t")
#space_vowels_period <- c("c","5","o","w","g","n","f","j","r","t")
#str_replace_all(raw.data1, space_vowels_period, "\ ")
```

### Based on above let's assume 'n' is space but our results are not encouraging (fragments too long), so we will try with 't' also, which is also disappointing for same reason
```{r}
str_replace_all(raw.data1,"n", "\ ")
```
```{r}
str_replace_all(raw.data1,"t", "\ ")
```
### Let's just try with various other elements we identified as 'space' candidates. But our results are similar.
```{r}
str_replace_all(raw.data1,"j", "\ ")
raw.data1
str_replace_all(raw.data1,"5", "\ ")
str_replace_all(raw.data1,"o", "\ ")
str_replace_all(raw.data1,"w", "\ ")
str_replace_all(raw.data1,"g", "\ ")
str_replace_all(raw.data1,"f", "\ ")
str_replace_all(raw.data1,"r", "\ ")
str_replace_all(raw.data1,"c", "\ ")

```
### Let's try another approach - try to find repeating 2 or 3 character sequences. (substitutes for of, in, the, and)
```{r}
sort(table(str_extract_all(raw.data1, ".{2}")), decreasing=TRUE)
sort(table(str_extract_all(raw.data1, ".{3}")), decreasing=TRUE)

```

### So let's search for most commonly used three letter words - 'and' and 'the'. For this let's what three letter groups are most repeating in the given messae.
```{r}
str_extract_all(raw.data1, "c..c")
str_extract_all(raw.data1, "5..5")
str_extract_all(raw.data1, "o..o")
str_extract_all(raw.data1, "w..w")
str_extract_all(raw.data1, "g..g")
str_extract_all(raw.data1, "n..n")
str_extract_all(raw.data1, "f..f")
str_extract_all(raw.data1, "j..j")
str_extract_all(raw.data1, "r..r")
str_extract_all(raw.data1, "t..t")
```
### Status : Unresolved. I would think 'space' is represented by a combination of characters. and following from that it is possible other characters are also represented by multiple characters.

