---
title: "Yelp Data Upload To Azure"
author: "JM"
date: "May 6, 2017"
output: html_document
---


Note -  RSQLServer deprecated. RODBC > RJDBC
 Download drivers.https://www.microsoft.com/en-us/download/details.aspx?id=50420
 

```{r}
library(RODBC)
library(jsonlite)
connectionString <- "Driver=ODBC Driver 13 for SQL Server;Server=tcp:data607yelp1.database.windows.net,1433;Database=DATA607_FinalProject_Yelp1;Uid=data607@data607yelp1;Pwd=XXX;Encrypt=yes;TrustServerCertificate=no;Connection Timeout=30;"
conn <- odbcDriverConnect(connectionString)
```

```{r eval=FALSE}
df <- stream_in(file("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/yelp_academic_dataset_business.json"), pagesize = 500, flatten=TRUE, simplifyDataFrame=TRUE)
sqlSave(conn, df, tablename="YelpBusiness", rownames=FALSE, append=TRUE)
```


```{r}
for(i in 1:9) {
  filename <- paste0("yelp_user0",i)
  filepath <- paste0("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/YelpUser/",filename)
  print(filepath)
  df <- stream_in(file(filepath), pagesize = 500, flatten=TRUE, simplifyDataFrame=TRUE)
  sqlSave(conn, df, tablename="YelpUser", rownames=FALSE, append=TRUE, verbose=FALSE, fast=TRUE)
}

df <- stream_in(file("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/YelpUser/yelp_user10"), pagesize = 500, flatten=TRUE, simplifyDataFrame=TRUE)
sqlSave(conn, df, tablename="YelpUser", rownames=FALSE, append=TRUE, verbose=FALSE, fast=TRUE)


```


```{r}
for(i in 0:9) {
  filename <- paste0("yelp_reviewn0",i)
  filepath <- paste0("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/YelpReview/",filename)
  print(filepath)
  dfr <- stream_in(file(filepath), pagesize = 5000, flatten=TRUE, simplifyDataFrame=TRUE)
  sqlSave(conn, dfr, tablename="YelpReview", rownames=FALSE, append=TRUE)
}

for(i in 28:40) {
  filename <- paste0("yelp_reviewn",i)
  filepath <- paste0("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/YelpReview/",filename)
  print(filepath)
  dfr <- stream_in(file(filepath), pagesize = 5000, flatten=TRUE, simplifyDataFrame=TRUE)
  sqlSave(conn, dfr, tablename="YelpReview", rownames=FALSE, append=TRUE)
}

for(i in 13,27,41) {
  filename <- paste0("yelp_reviewn",i)
  filepath <- paste0("C:/Jai/MSDA/MSDA_JM/DATA607/Yelp/YelpReview/",filename)
  print(filepath)
  dfr <- stream_in(file(filepath), pagesize = 5000, flatten=TRUE, simplifyDataFrame=TRUE)
  sqlSave(conn, dfr, tablename="YelpReview", rownames=FALSE, append=TRUE)
}

